Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
simple conclusion

\subsection{Collect naming data with controlled specificity}

Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to gather

@@

>>>>

\subsection{Collect naming data with controlled level of specificity}

Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to be able to systematically gather object names at the sub-level.

@@

\section{Conclusion}

In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
The comparison between different data sets and available annotations for them reveals that consist procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to use of concepts) turns out to be difficult.
